Milk intake and risk of mortality risk in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-06-25 Paperfolder/Paperfolder.Rmd
updated table 2 40% men

@@

dt <- read.csv("tab/tab1.csv", header = T)
names(dt) <- c("", "Never", "Drinker", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Daily", "P value")

@@

\hspace{1em}Exercise (> 1h/week), \% & 19 & 27.6 & 26.5 & 25 & 25.5 & 29.5 & <0.001\\

@@

\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48 & 47.5 & 52.9 & <0.001\\
\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31 & 36.6 & <0.001\\

@@

\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25 & 24.6 & 24.2 & 34.8 & <0.001\\
\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\

@@

\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34 & <0.001\\

@@

\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20 & <0.001\\

@@

## Subsection Heading Here

@@

### Subsubsection Heading Here

@@

```{r tab1, echo=FALSE, eval=TRUE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/HRAFTweib.csv", header = T)
names(dt) <- c("Milk intake", "Median", "Mean (SD)", "95% CrI", "MCSE", "Probability", "Median", "Mean (SD)", "95% CrI", "MCSE")
kable(dt, format = "latex", caption = "", booktabs = T,linesep = "") %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  add_header_above(c(" ", "Hazard ratio (HR)" = 5, "Acceleration factor (AF)" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", " Probability indicates that the p for HR smaller than 1."))
```

>>>>

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 957 were cerebral infarction (520 men and 437 women), and 952 were hemorrhagic stroke (432 men and 520 women).

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who chose "never" as their milk intake frequency at the baseline, milk drinkers were less likely to be a current smoker or a daily alcohol consumer in both men and women. Furthermore, people consumed milk more than 1-2 times/month were more likely to be a daily consumers of vegetable, fruit  as well as coffee, and more likely to join exercise more than 1 hour/week among either sex.

Table

@@

dt <- read.csv("tab/tab1.csv", header = T)
names(dt) <- c("", "Never", "Drinker", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily", "P value")

@@

\hspace{1em}Exercise (> 1h/week), \% & 19.0 & 27.6 & 26.5 & 25.0 & 25.5 & 29.5 & <0.001\\

@@

\rowcolor{gray!6}  \hspace{1em}Coffee intake, daily, \% & 43.8 & 50.7 & 50.5 & 48.0 & 47.5 & 52.9 & <0.001\\
\hspace{1em}Educated over 18 years old, \% & 25.5 & 34.7 & 33.8 & 33.3 & 31.0 & 36.6 & <0.001\\

@@

\hspace{1em}Vegetable intake, daily, \% & 24.7 & 30.4 & 25.0 & 24.6 & 24.2 & 34.8 & <0.001\\
\rowcolor{gray!6}  \hspace{1em}Fruit intake, daily, \% & 25.0 & 35.7 & 26.6 & 29.2 & 29.2 & 41.1 & <0.001\\

@@

\hspace{1em}Educated over 18 years old, \% & 19.9 & 31.6 & 27.9 & 29.8 & 27.4 & 34.0 & <0.001\\

@@

\hspace{1em}History of hypertension, \% & 21.5 & 19.7 & 20.5 & 19.1 & 18.9 & 20.0 & <0.001\\

@@

<!-- ## Subsection Heading Here -->

@@

<!-- ### Subsubsection Heading Here -->

@@

```{r tab2, echo=FALSE, eval=TRUE, message=FALSE}
library(knitr)
library(kableExtra)
dt <- read.csv("tab/HRAFTweib.csv", header = T)
# dt <- data.frame(`Stroke` = c(rep("Total stroke", 15)), dt)
names(dt) <- c(" ", "Never", "1-2 times/Month", "1-2 times/Week", "3-4 times/Week", "Almost Daily")

kable(dt, format = "latex", caption = "Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.", booktabs = T, linesep = "") %>%
    # collapse_rows(columns = 1, valign = "top") %>% 
  pack_rows("Model 0", 4, 7) %>%
  pack_rows("Model 1", 8, 11) %>%
  pack_rows("Model 2", 12, 15) %>%
kable_styling(latex_options = c("striped","hold_position"), font_size = 8) %>%
  # add_header_above(c(" ", "Estimated HR in Men" = 4, "Estimated HR in Women" = 4)) %>% 
  footnote(c("Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;", "Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1."))

```

### 2020-06-25 Paperfolder/Paperfolder.tex
updated table 2 40% men

@@

\hypertarget{subsection-heading-here}{%
\subsection{Subsection Heading Here}\label{subsection-heading-here}}

\hypertarget{subsubsection-heading-here}{%
\subsubsection{Subsubsection Heading
Here}\label{subsubsection-heading-here}}

@@

\caption{\label{tab:tab1}}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Hazard ratio (HR)} & \multicolumn{4}{c}{Acceleration factor (AF)} \\
\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-10}
Milk intake & Median & Mean (SD) & 95\% CrI & MCSE & Probability & Median & Mean (SD) & 95\% CrI & MCSE\\
\midrule
\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & \vphantom{2} -\\
1-2 t/Mon & 0.88 & 0.89 (0.09) & (0.73, 1.08) & 0.0022 & 86.50\% & 0.93 & 0.93 (0.06) & (0.81, 1.06) & 0.0016\\
\rowcolor{gray!6}  1-2 t/Week & 0.77 & 0.77 (0.07) & (0.63, 0.91) & 0.0019 & 99.90\% & 0.83 & 0.83 (0.05) & (0.73, 0.94) & 0.0014\\
3-4 t/Week & 0.79 & 0.79 (0.07) & (0.66, 0.94) & 0.0022 & 99.70\% & 0.85 & 0.85 (0.05) & (0.74, 0.96) & 0.0016\\
\rowcolor{gray!6}  Daily & 0.90 & 0.90 (0.06) & (0.79, 1.03) & 0.0018 & 93.47\% & 0.93 & 0.93 (0.04) & (0.85, 1.02) & 0.0013\\
Never & - & - & - & - & - & - & - & - & \vphantom{1} -\\
\rowcolor{gray!6}  1-2 t/Mon & 0.98 & 0.98 (0.11) & (0.79, 1.19) & 0.0027 & 58.70\% & 0.99 & 0.99 (0.06) & (0.87, 1.11) & 0.0016\\
1-2 t/Week & 0.84 & 0.84 (0.08) & (0.70, 1.00) & 0.0022 & 97.31\% & 0.90 & 0.90 (0.05) & (0.81, 1.00) & 0.0014\\
\rowcolor{gray!6}  3-4 t/Week & 0.85 & 0.86 (0.08) & (0.71, 1.02) & 0.0021 & 96.05\% & 0.91 & 0.91 (0.05) & (0.82, 1.01) & 0.0013\\
Daily & 0.75 & 0.76 (0.05) & (0.66, 0.87) & 0.0016 & 100.00\% & 0.85 & 0.85 (0.04) & (0.78, 0.92) & 0.0011\\
\rowcolor{gray!6}  Never & - & - & - & - & - & - & - & - & -\\
1-2 t/Mon & 1.00 & 1.01 (0.12) & (0.81, 1.24) & 0.0041 & 50.61\% & 1.00 & 1.00 (0.07) & (0.88, 1.14) & 0.0029\\
\rowcolor{gray!6}  1-2 t/Week & 0.86 & 0.87 (0.09) & (0.72, 1.05) & 0.0036 & 93.73\% & 0.92 & 0.92 (0.06) & (0.82, 1.03) & 0.0024\\
3-4 t/Week & 0.89 & 0.90 (0.09) & (0.74, 1.08) & 0.0038 & 89.62\% & 0.93 & 0.94 (0.06) & (0.84, 1.05) & 0.0026\\
\rowcolor{gray!6}  Daily & 0.80 & 0.80 (0.07) & (0.69, 0.93) & 0.0031 & 99.04\% & 0.88 & 0.88 (0.05) & (0.81, 0.96) & 0.0020\\
\bottomrule
\multicolumn{10}{l}{\textit{Note: }}\\
\multicolumn{10}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
\multicolumn{10}{l}{ Probability indicates that the p for HR smaller than 1.}\\
\end{tabular}
\end{table}

>>>>

The total follow-up was 1555073 person-years (median = 19.3 years),
during which 2675 death from stroke was confirmed (1352 men and 1323
women). Among these stroke mortality, 957 were cerebral infarction (520
men and 437 women), and 952 were hemorrhagic stroke (432 men and 520
women).

As listed in \textbf{Table \ref{tab:tab1f}}, compared with those who
chose ``never'' as their milk intake frequency at the baseline, milk
drinkers were less likely to be a current smoker or a daily alcohol
consumer in both men and women. Furthermore, people consumed milk more
than 1-2 times/month were more likely to be a daily consumers of
vegetable, fruit as well as coffee, and more likely to join exercise
more than 1 hour/week among either sex.

Table

@@

@@

\caption{\label{tab:tab2}Summary of posterior Hazard Ratios (HR) of mortality from total stroke, different stroke type according to the frequency of milk intake in men.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllll}
\toprule
  & Never & 1-2 times/Month & 1-2 times/Week & 3-4 times/Week & Almost Daily\\
\midrule
\rowcolor{gray!6}  Person-year & 135704 & 56551 & 97098 & 92153 & 252364\\
N & 8508 & 3522 & 5928 & 5563 & 15865\\
\rowcolor{gray!6}  Total Stroke & 326 & 122 & 181 & 177 & 546\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 0}}\\
\hspace{1em}MeanHR (SD) & - & 0.89 (0.09) & 0.77 (0.07) & 0.79 (0.07) & 0.90 (0.06)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.73, 1.08) & (0.63, 0.91) & (0.66, 0.94) & (0.79, 1.03)\\
\hspace{1em}MCSE & - & 0.0022 & 0.0019 & 0.0022 & 0.0018\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 86.50\% & 99.90\% & 99.70\% & 93.47\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 1}}\\
\hspace{1em}MeanHR (SD) & - & 0.98 (0.11) & 0.84 (0.08) & 0.86 (0.08) & 0.76 (0.05)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.79, 1.19) & (0.70, 1.00) & (0.71, 1.02) & (0.66, 0.87)\\
\hspace{1em}MCSE & - & 0.0027 & 0.0022 & 0.0021 & 0.0016\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 58.70\% & 97.31\% & 96.05\% & 100.00\%\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Model 2}}\\
\hspace{1em}MeanHR (SD) & - & 1.01 (0.12) & 0.87 (0.09) & 0.90 (0.09) & 0.80 (0.07)\\
\rowcolor{gray!6}  \hspace{1em}95\% CrI & - & (0.81, 1.24) & (0.72, 1.05) & (0.74, 1.08) & (0.69, 0.93)\\
\hspace{1em}MCSE & - & 0.0041 & 0.0036 & 0.0038 & 0.0031\\
\rowcolor{gray!6}  \hspace{1em}Pr(HR < 1) & - & 50.61\% & 93.73\% & 89.62\% & 99.04\%\\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviations: SD, standard deviation; CrI, credible interval; MCSE, Monte Carlo Standard Error;}\\
\multicolumn{6}{l}{Pr(HR < 1) indicates the prabability for posterior HR to be smaller than 1.}\\
\end{tabular}
\end{table}
